### 2014-10-09 writing/AAAI SSS '15/methods.tex
Create AAAI paper directory
Minor update

\section{Recursive neural network models} \label{methods}

We study neural models that adhere to the linguistic \ii{principle of
 compositionality}, which says that the meanings for complex
expressions are derived from the meanings of their constituent parts
via specific composition functions \cite{Partee84,Janssen97}. In our
distributed setting, word meanings are vectors of length $n$. The
composition function maps pairs of them to single vectors of length $n$, 
which can then be merged again to represent more complex
phrases. Once the entire sentence-level representation has been
derived, it serves as a fixed-length input for some subsequent function.

We use the model architecture proposed in \cite{bowman2013can} and
depicted in Figure~\ref{sample-figure}. The two phrases being compared
are built up separately on each side of the tree, using the same
composition function, until they have each been reduced to single
vectors. The resulting vectors are fed into a separate comparison
layer that is meant to generate a feature vector capturing the
relation between the two phrases. The output of this layer is then
given to a softmax classifier, which in turn produces a hypothesized
distribution over the seven relations represented in Table~\ref{b-table}.

For a composition layer, we evaluate models with both the plain neural
network layer function \eqref{rnn} and the RNTN layer function
\eqref{rntn} proposed in \citet{chen2013learning}. A sigmoid
nonlinearity (element-wise $\tanh$) is applied to the output of either
layer function, following \cite{socher2013acl1}.
%
\begin{gather} \label{rnn}
\vec{y}_{\textit{RNN}} = f(\mathbf{M} [\vec{x}^{(l)}; \vec{x}^{(r)}] + \vec{b}) \\ % TODO: Add column vectors?
\label{rntn}
\vec{y}_{\textit{RNTN}} = f(\vec{x}^{(l)T} \mathbf{T}^{[1 \ldots n]} \vec{x}^{(r)} + \mathbf{M} [\vec{x}^{(l)}; \vec{x}^{(r)}] + \vec{b})
\end{gather} 
%
Here, $\vec{x}^{(l)}$ and $\vec{x}^{(r)}$ are the column vector
representations for the left and right children of the node, and
$\vec{y}$ is the node's output.  The RNN concatenates them, multiplies
them by an $n \times 2n$ matrix of learned weights, and applies the
element-wise non-linearity to the resulting vector. The RNTN has the
same basic structure, but with the addition of a learned third-order
tensor $\mathbf{T}$, dimension $n \times n \times n$, modeling
multiplicative interactions between the child vectors. Both models
include a bias vector, represented as $\vec{b}$.

@@

\begin{figure}[tp]
  \centering
 % \includegraphics[scale=0.35]{model.eps}
  \input{figure1}
  \caption{The model structure used to compare \ii{((all reptiles) walk)} and \ii{((some turtles) move)}. 
    The same structure is used for both the RNN and RNTN layer functions.} 
  \label{sample-figure}
\end{figure}

>>>>

\subsection*{Neural network models for relation classification} \label{methods}

% TODO: Should we cite our NIPS manuscript?

We follow the approach to learning semantically meaningful embeddings 
proposed in \cite{bowman2013can}, which is centered on the problem of
labeling a pair of words or sentences with one of a small set of logical
relations. The architecture of the model that we use is depicted in
Figure~\ref{sample-figure}. The model represents the two

The two phrases being compared
are built up separately on each side of the tree, using the same
composition function, until they have each been reduced to single
vectors. The resulting vectors are fed into a separate comparison
layer that is meant to generate a feature vector capturing the
relation between the two phrases. The output of this layer is then
given to a softmax classifier, which in turn produces a hypothesized
distribution over the seven relations represented in Table~\ref{b-table}.

For a composition layer, we evaluate models with both the plain neural
network layer function \eqref{rnn} and the RNTN layer function
\eqref{rntn} proposed in \citet{chen2013learning}. A sigmoid
nonlinearity (element-wise $\tanh$) is applied to the output of either
layer function, following \cite{socher2013acl1}.
%
\begin{gather} \label{rnn}
\vec{y}_{\textit{RNN}} = f(\mathbf{M} [\vec{x}^{(l)}; \vec{x}^{(r)}] + \vec{b}) \\ % TODO: Add column vectors?
\label{rntn}
\vec{y}_{\textit{RNTN}} = f(\vec{x}^{(l)T} \mathbf{T}^{[1 \ldots n]} \vec{x}^{(r)} + \mathbf{M} [\vec{x}^{(l)}; \vec{x}^{(r)}] + \vec{b})
\end{gather} 
%
Here, $\vec{x}^{(l)}$ and $\vec{x}^{(r)}$ are the column vector
representations for the left and right children of the node, and
$\vec{y}$ is the node's output.  The RNN concatenates them, multiplies
them by an $n \times 2n$ matrix of learned weights, and applies the
element-wise non-linearity to the resulting vector. The RNTN has the
same basic structure, but with the addition of a learned third-order
tensor $\mathbf{T}$, dimension $n \times n \times n$, modeling
multiplicative interactions between the child vectors. Both models
include a bias vector~$\vec{b}$.

@@

\begin{figure}[tp]
  \centering
  \input{figure1}
  \caption{The model structure used to compare \ii{turtle} and \ii{animal}. 
    The same structure is used for both the RNN and RNTN layer functions.} 
  \label{sample-figure}
\end{figure}

### 2014-10-09 writing/AAAI SSS '15/wordnet.tex
Minor update

% TODO: Describe use of GloVe once there are clearer results. Should we omit mention of it entirely?

\begin{table}[h]
\centering\resizebox{4in}{!}{\small
  \setlength{\tabcolsep}{15pt}
  \renewcommand{\arraystretch}{1.1}
  \begin{tabular}{l c l l} 
    \toprule
    Comparison layer & \% training data & w/ GloVe & w/o GloVe \\
    NN       & 100\%   & TODO & TODO \\
    NN       & 75\%   & 98.6 (100.0) & TODO \\
    NN       & 33\%   & TODO & 37.0 (37.0) \\ % TODO: See if this improves
    NN       & 16\%   & TODO & 92.0 (100.0)\\
    NTN       & 100\%   & 99.6 (100.0) & 99.4 (99.9) \\
    NTN       & 75\%   & 98.6 (100.0) & TODO\\
    NTN       & 33\%   & 95.1 (99.8) & 95.2 (100.0) \\
    NTN       & 16\%   & 94.6 (100.0) & 92.1 (100.0) \\
    \bottomrule
  \end{tabular}}
 \caption{Test (train) accuracy figures on the WordNet data.\label{b-table}}  
\end{table}

>>>>

% TODO: Describe use of GloVe once there are clearer results. Since it doesn't look like it makes a huge difference,
% should we perhaps just omit mention of it entirely to save space?

\begin{table}[h]
\centering\resizebox{4in}{!}{\small
  \setlength{\tabcolsep}{15pt}
  \renewcommand{\arraystretch}{1.1}
  \begin{tabular}{l c l l} 
    \toprule
    Comparison layer & \% training data & w/ GloVe & w/o GloVe \\
    Most frequent class & -- & 37.9 (--) & 37.9 (--) \\
    NN       & 100\%   & TODO & TODO \\
    NN       & 75\%   & 98.6 (100.0) & TODO \\
    NN       & 33\%   & TODO & 37.0 (37.0) \\ % TODO: See if this improves
    NN       & 16\%   & TODO & 92.0 (100.0)\\
    NTN       & 100\%   & 99.6 (100.0) & 99.4 (99.9) \\
    NTN       & 75\%   & 98.6 (100.0) & TODO\\
    NTN       & 33\%   & 95.1 (99.8) & 95.2 (100.0) \\
    NTN       & 16\%   & 94.6 (100.0) & 92.1 (100.0) \\
    \bottomrule
  \end{tabular}}
 \caption{Test (train) accuracy figures on the WordNet data.\label{b-table}}  
\end{table}
